A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-18 writeup/paper.tex
Modified Overview
Rephrased the last paragraph as questions to make it a little more
interesting.

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[numbers]{natbib}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

@@

%We construct a task in which we aim to build bilingual dictionaries for over 100 languages, containing over 10,000 words each, using only translators available on Mechanical Turk. We collect demographic data relevant to the workers' language skills, and evaluate the quality of the translations submitted from workers across varying backgrounds and locations. Based on the data collected, we identify the strengths of Mechanical Turk as a source of multilingual data, and discuss best practices for ensuring high data quality from non-professional translators.

The demographic data allows us to analyze current speaker populations for more than 100 languages.  Our survey also allows us to report on other information like how quickly translations were completed for each language, how often workers misrepresented their language abilities to try to obtain financial rewards, and what the estimated accuracy is for the bilingual dictionaries that we construct.

>>>>

\documentclass[11pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage[numbers]{natbib}
\usepackage[fit]{truncate}
\usepackage{acl2012}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{url}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{multirow}
\usepackage{dblfloatfix}
\usepackage{float}
\usepackage{subfigure}
\DeclareMathOperator*{\argmax}{arg\,max}
\setlength\titlebox{5.4cm}    % Expanding the titlebox

@@

The survey data allows us to analyze current speaker populations for more than 100 languages.  The data also allows us to answer questions like: 
How quickly is work completed in a given language? 
Are crowdsourced translations reliably good? 
How often do workers misrepresented their language abilities to falsely obtain financial rewards?
